Flowchart of Current Algorithm

### 2008-10-13 docs/flowchart/paper.tex
added dpdt factor part to w0 equations

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh},$ \MarginPar{note: this is true only for plane-parallel}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}

@@

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}),

\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} =  \overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}} \psi^{\nph,\star} \enskip , \nonumber
\end{equation}
for plane-parallel geometries, where 
$\gammabar^{\nph,\star} = (\gammabar^{n} + \gammabar^{n+1,\star} ) / 2 $ and
$ p_0^{\nph,\star} = (p_0^{n} + p_0^{n+1,\star} ) / 2.$

>>>>

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh}$ and the volume discrepancy correction with $f=0.3$:
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}}
\left[ \psi^{\nmh} - f \left(\frac{p_0^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n} \right)\right]
\enskip . \nonumber
\end{equation}

@@

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}) with the 
volume discrepancy correction with $f=0.3$:
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = 
\overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left[ \psi^{\nph,\star} - f \left(\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right)\right]
\enskip , \nonumber
\end{equation}
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}
\end{equation}
\begin{equation}
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}
\end{equation}
\begin{equation}
\overline{p(\rho,h,X_k)^{\nph,\star}} = 
\frac{\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}}{2}
\end{equation}
